\chapter{\huge{\textbf{Conclusion of Study and Future Works}}}

\section{\textbf{Introduction}}
This chapter presents conclusions, future works within the field of innovation within the performance of public universities in Nairobi.
\section{\textbf{Conclusion}}
This study geared toward finding the link between innovation and performance of public universities in capital of Kenya. the particular objectives of the study were to determine the character of innovative enhancements with within the general public universities, in capital of Kenya and confirm the have a bearing on of innovative enhancements on the performance of public universities in capital of Kenya. The population for the study was the general public universities in capital of Kenya from that the sample was designated. The scientist adopted descriptive survey style. knowledge to determine the link was obtained with the utilization of structured questionnaires. Data analysis was done using multi hierarchical regression model.

The universities had deviated from the normal ways in which to giving education and engaged in creation of latest and important informative ways in which. The study results reveal that there's a robust positive relationship between innovation indicators and also the performance of the general public universities. The results more demonstrate that an out sized proportion of the general public universities performance is accounted for by combined impact of innovation.

The study results reveal that there's a robust positive relationship between innovation and also the resource generation of the colleges. this means that the symptoms of resource generation like fund levels, costs/cost saving, ICT facilities, physical facilities and equipment’s, performance appraisals for the workers, worker satisfaction and client satisfaction are determined by the innovations of the general public universities. It reveals that a rise within the level of technology like ICT facilities results into adequate resource allocation since the potency is increased.

\section{\textbf{Future Works}}
There is would like for future analysis to incorporate different universities that weren't sampled during this study. Non-public universities ought to even be studied within the same study space. Another potential space of study would get on the factors that have an effect on the performance of public universities different that innovation.

The study used the cross sectional survey style. Future analysis will adopt completely different styles like longitudinal survey that might trace the influence of innovation on the structure performance over a amount of your time. The research worker will adopt case study so as to urge deeper info on the influence of innovation on structure performance. Future studies might also adopt different analysis tools to reveal the connection established during this study.

