\chapter{\huge{\textbf{Introduction}}}

\section{\textbf{Hypothesis and Research Problem}}
We based our research thesis on the research problem; "Does infrastructure and facilities in Nairobi Universities maximize innovation among students and stuff in the Technological industry?”

From the research problem we derived the following hypothesis; "Lack of appropriate facilities and infrastructure hinder innovation among students and stuff in Nairobi Universities." Our hypothesis was derived from previous research.

\section{\textbf{Value of the Study}}
Innovation is one of the key factors in control practices of an organisation. Management exercise refers to the system of approach formulation, implementation, assessment and control primarily based totally on micro and macro surroundings factors. It includes identity of the organisation's functions, it calls for plans, and movements got down achieving the purpose.

Upon the wake of the twenty first century, university schooling has come to be most of the offerings extensively sought i.e. the call for university schooling has been at pleasant rapid growing. For public establishments to stay green and powerful within side the converting and aggressive environment, it has come to be a simple requirement for them to undertake control practices of their operations. For establishments of better studying to stay aggressive and gain ever-growing expectations, they ought to have the ability to put into effect control models.

The Higher Education region all over the arena has within side the beyond few years witnessed extended increase in phrases of extended pupil enrolment, extended variety of latest establishments, and increase and enlargement of applications offered. The changes, surroundings and the challenges that better schooling establishments are going through nowadays are severe and complex.

Failure to undertake and implement control practices with the aid of using Universities has resulted to masses of demanding situations inclusive of negative or no infrastructures, negative provider transport educational staffs, demanding situations of accreditation, bad contention amongst control and staff, deteriorating best of training amongst others. In Africa, a multiplied enlargement in universities is followed with the aid of using increasing enrolment of university students and applications offered, and converting modes of financing. This has resulted too many control demanding situations and as a result a want for reforms and institutional restructuring.

In Nairobi because of the emergence of many universities, the overall performance and provider shipping of those institutions were adversely affected. Competition within side the Nairobi Education zone has accelerated. Funding from the authorities has faded and consequently posed demanding situations in outfitting university budgets, making plans and control. Consequently, the variety of universities has notably accelerated and demands the adoption of control practices and measures for assessing institution's overall performance.

\section{\textbf{Research Objectives}}
The overall goal of the observe changed into to set up the innovation and performance of public universities in Nairobi. The particular goals of this observe have been to:
\begin{enumerate}

    \item Establish the character of innovative improvements with inside the public universities, in Nairobi.
    
    \item Determine the have an impact on of innovative improvements on the overall performance of public universities in Nairobi.
    
\end{enumerate}



