\chapter{\huge{\textbf{Literature Review }}}

\section{\textbf{Problem and purpose of the study}}
The call for university schooling in Kenya has increased considerably and has outpaced supply. There is an increased increase in student numbers in universities has now no longer been marched with the aid of using enlargement of physical centres and educational infrastructure and a number of the prevailing infrastructure became in insufficient and dilapidated. Universities in Nairobi are required with the aid of using regulation to provide suitable and adequate centres to cater for the number of programmes on offer and students’ enrolment. These consist of library and Information Communication Technology (ICT) infrastructure. Those universities that do not comply are critically restricted.  High trendy studies infrastructures are essential to the fulfilment of any university. This chapter explores the modern-day state and tendencies in studies infrastructure, in phrases of library and ICT centres. The chapter specially looks at insights into the modern-day state of ICT infrastructure in Nairobi universities; the adequacy of budget allocated for ICT; in addition to the demanding situations libraries and ICT gadgets in Nairobi universities face.

\section{\textbf{Introduction on University Education and National Development}}
After independence, the call for university training in Nairobi has persevered to increase. Public universities have been absolutely funded via way of means of the authorities and nonetheless get hold of maximum in their funding from the authorities despite the fact that they are an increasing number of supplementing this with lessons costs mainly from university students at the parallel diploma programs. Parallel diploma programs; have been particularly added in universities for generating money. This is the approach of admitting complete fee-paying university students over and above the scholars who are admitted with authorities’ subsidy.

Unfortunately, the universities have persevered to stand severe economic problems. In the beyond few years, they have been working on a Sh9 Billion deficit, a state of affairs that has persevered to undermine their capacity to provide fine training and education and to conduct research. Even as investment drops, enrolment numbers have persevered to soar.

As many researchers have clearly indicated, financing of universities is turning into an increasing number of tough for a quantity of reasons:
\begin{itemize}

    \item The public quarter is difficult pressed with responsibilities especially at the switch aspect of the budget (e.g. getting to an ageing population, fitness care, poverty, and overseas aid), as nicely as with safety troubles and the renovation of public infrastructure. Consequently, the proportion of the sales being committed to university training is sure to diminish.
    \item The fee of imparting university schooling and of doing studies keeps developing significantly.
    
\end{itemize}

The mixture of excessive enrolments and coffee investment has hit even installed universities hard. Most of the universities do now no longer have sufficient first rate coaching or studying centres or get right of entry to modern era and because of this coaching frequently does now no longer boost past conventional methods.

\section{\textbf{Technological Sector in Nairobi}}
Being the ICT hub of the East African region, Kenya’s ICT quarter will account for as much as 7\% of the GDP. Consistent with that is the Kenya 2030 imaginative and prescient to end up a competitive middle-earnings country. The three pillars (economic, social and political) have generation and innovation because the foundation.

The Second Medium Term Plan for 2030, which ran among 2013, and 2017 recommends intensifying the coordination of innovation, studies improvement and commercialization as a flagship programme for sustained productiveness growth. If this plan become nicely carried, out and is an extraordinary query as one might say the execution of commercialization of technological innovation within side the united states has been minimal. Absence of adequate infrastructure and suitable regulatory coverage frameworks are simply however a few of the significance of things that clearly assist this claim.

Kenyan universities and especially the ones within side the capital of Nairobi have to be at the middle of the countrywide schedule to have a sustainable aggressive economic system that is primarily based totally on technology. Universities should develop the studying reports of the students. The technological enterprise stretches throughout all monetary sectors and this must be contemplated within side the first-rate of schooling undertaken via way of means of the incoming workforce. A shift of idea is consequently urgently wanted from get entry to first-rate or extra precisely, toward get entry to with first-rate since universities have a vital position to play in fostering paintings skills, technological innovation, engagement and countrywide development.

\section{\textbf{Innovation in Nairobi Universities}}
There are distinct definitions of innovations. One instance may be the search for locating new approaches of doing things. Another instance of a definition of innovation is the success exploitation of new thoughts. In each definitions, a great deal awareness is placed on innovation as a manner through which establishments can stable an aggressive side over their opponents in globally aggressive environments both through exploring new thoughts and through locating new approaches to perform tasks.

The call for university education in Nairobi has accelerated appreciably and has outpaced supply. The Public Universities Inspection Board stated that multiplied boom in scholar numbers in universities has now no longer been matched with the aid of using growth of bodily centres and instructional infrastructure and a number of the present infrastructure turned into inadequate and dilapidated. Universities in Nairobi are required with the aid of using regulation to provide suitable and ok centres to cater for the wide variety of programs on provide and students’ enrolment. These encompass library and Information Communication Technology (ICT) infrastructure. Those universities that do not comply are significantly restricted.  High popular studies infrastructures are essential to the fulfilment of any university.

\section{\textbf{Infrastructure in Nairobi Universities: Targeting Nairobi University}}
According to the University of Nairobi, the college’s ICT infrastructure and assets have grown enormously over the past decade to cowl all campuses and extra-mural centres. The college has endured to decorate its ICT infrastructure to satisfy the developing call for and make sure that records is processed and made handy to all applicable stakeholders the use of the most powerful means. Among those enhancements, the University is remodelling the Data Centre into an Educational Data Centre in order to now no longer best make sure capacity, availability, and safety of computing assets, however can even affirm the University of Nairobi’s lead role via way of means of growing an EDC in order to be a centre of excellence in education on information centre technologies. The college has additionally collaborated with KENET (Kenya Education Network Trust – The National Research Network) to offer broadband connectivity on fibre that has ensured speedy and reliable get admission to on-line assets from every of its campuses unfold throughout eighteen places in Nairobi, and different towns within side the country. In addition, the section is eager to increase WIFI offerings to scholar hostels and not unusual place regions to decorate on-line get admission to assets.

Prior studies discovered out that ICT gadgets and libraries in instructional establishments in Nairobi face some of demanding situations which includes excessive expenses of obtaining and upgrading the modern-day structures; insufficient staff; unreliable Internet access; loss of modern-day and applicable studying assets; loss of suitable furniture; area constraints; vandalism and insufficient funding. The library is of no use if it does now no longer have appropriate statistics materials. For the college library to guide the venture of the institution, its miles required to frequently acquire enough modern-day and applicable statistics materials. Inadequate funding, insufficient staffing, and absence of centres or infrastructure are the greatest obstacles to adoption of Open Access (OA). The college libraries are overcrowded whilst e-book collections are previous and insufficient. The library centres and statistics structures in nearly all the colleges are antiquated with books and scholarly journals, which are not simplest few however also vintage and consequently inappropriate to the modern-day wishes and priorities. There is a loss of applicable books, insufficient use of the Internet and trendy loss of studying area created the foremost constraints to scholar studying. The loss of ok studying assets posed a project to college students studying habits. Appearance of ICT on the worldwide scene has induced a revolution in libraries and the simplest manner to fulfil customers call for is to apply ICT in statistics service delivery.
